prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-07-06 inst/MyArticle/paper.Rmd
simplify

Using a benchmark dataset whose ground truth is known (see Methods), we assessed the performance of different modeling approaches implemented in `r BiocStyle::Githubpkg("fgcz/prolfqua")` (Tables \@ref(tab:prolfquaModels) and \@ref(tab:describeBenchmarkedModels)), `r BiocStyle::Biocpkg("MSstats")` and `r BiocStyle::Biocpkg("proDA")`. Table \@ref(tab:describeBenchmarkedModels) summarizes which methods we have evaluated, which MaxQuant results we used, and if the models are fitted to peptide or protein intensities. We make the R-markdown files to replicate the benchmarking available at `r BiocStyle::Githubpkg("wolski/prolfquabenchamrk")` and at [BenchmarkingIonstarData](https://wolski.github.io/prolfquabenchmark).

@@

# read combined_protein.tsv 
protein <- prolfqua::tidy_MSFragger_combined_protein(protein)
# remove proteins identified by a single peptide
protein <- protein |> dplyr::filter(unique.stripped.peptides > 1)

>>>>

Using a benchmark dataset whose ground truth is known (see Methods), we assessed the performance of different modeling approaches implemented in `r BiocStyle::Githubpkg("fgcz/prolfqua")` (Tables \@ref(tab:prolfquaModels) and \@ref(tab:describeBenchmarkedModels)), `r BiocStyle::Biocpkg("MSstats")` and `r BiocStyle::Biocpkg("proDA")`. Table \@ref(tab:describeBenchmarkedModels) summarizes which methods we have evaluated, which MaxQuant results we used, and if the models are fitted to peptide or protein intensities. We make the R-markdown files to replicate the benchmarking available at `r BiocStyle::Githubpkg("wolski/prolfquabenchmark")`.

@@

# read combined_protein.tsv 
protein <- prolfqua::tidy_MSFragger_combined_protein_deprec(protein)
# remove proteins identified by a single peptide
protein <- protein |> dplyr::filter(unique.stripped.peptides > 1)
